---
title: "Speed Dating: How to get men to like women | Ruoxuan Gong and Francisco Mendoza"
output: html_notebook
---

```{r}
library(data.table)
library(ggplot2)
library(psych)
library(VIM)
library(mice)
```

```{r}
#access files
rounds <- fread('rounds.csv', sep=',')
participants <- fread('participants.csv',sep=',')
```

```{r}
str(rounds)
```

```{r}
#change variable types
rounds$same_country <- as.numeric(as.character(rounds$same_country))
rounds$diff_pref_attractive <- as.numeric(as.character(rounds$diff_pref_attractive))
rounds$diff_pref_sincere <- as.numeric(as.character(rounds$diff_pref_sincere))
rounds$diff_pref_intelligent <- as.numeric(as.character(rounds$diff_pref_intelligent))
rounds$diff_pref_fun <- as.numeric(as.character(rounds$diff_pref_fun))
rounds$diff_pref_ambitious <- as.numeric(as.character(rounds$diff_pref_ambitious))
rounds$diff_pref_sharedhobbies <- as.numeric(as.character(rounds$diff_pref_sharedhobbies))
#count total number of rows
nrow(rounds)
```

NA HANDLING
```{r}
#check how many NAs are there
#summary(rounds)
mice_plot <- aggr(rounds, col = c('navyblue','yellow'), numbers = T, sortVars = T,labels = names(rounds), cex.axis = .7, gap=3, ylab = c("Missing data","Pattern"))
```

```{r}
#removal of rows with incomplete cases
rounds.nona <- rounds[complete.cases(rounds),]
nrow(rounds.nona)
names(rounds.nona)
```

```{r}
#store indexes in a variable
rounds.nona.char <- rounds.nona[,c(1,3,4,5,7,8)]
#store numerical data
rounds.nona <- rounds.nona[,c(2,6,9:32)]
rounds.nona$rating_by_partner_attractive <- rounds.nona$rating_by_partner_attractive/10
rounds.nona$rating_by_partner_sincere <- rounds.nona$rating_by_partner_sincere/10
rounds.nona$rating_by_partner_intelligent <- rounds.nona$rating_by_partner_intelligent/10
rounds.nona$rating_by_partner_fun <- rounds.nona$rating_by_partner_fun/10
rounds.nona$rating_by_partner_ambitious <- rounds.nona$rating_by_partner_ambitious/10
rounds.nona$rating_by_partner_sharedhobbies <- rounds.nona$rating_by_partner_sharedhobbies/10

rounds.nona$rated_partner_attractive <- rounds.nona$rated_partner_attractive/10
rounds.nona$rated_partner_sincere <- rounds.nona$rated_partner_sincere/10
rounds.nona$rated_partner_intelligent <- rounds.nona$rated_partner_intelligent/10
rounds.nona$rated_partner_fun <- rounds.nona$rated_partner_fun/10
rounds.nona$rated_partner_ambitious <- rounds.nona$rated_partner_ambitious/10
rounds.nona$rated_partner_sharedhobbies <- rounds.nona$rated_partner_sharedhobbies/10
str(rounds.nona)
```


```{r}
#get the correlation coefficients...
#looks like there are no glaring correlation coefficients we need to worry about
M <- cor(rounds.nona)
round(M, digits = 3)
corrplot::corrplot(M, type = 'lower', diag = F)
#pairs.panels(rounds.nona)
```

```{r}
as.matrix(M)
```


ASSUMPTIONS OF LOGISTIC REGRESSION:
- Does not need a linear relationship between the dependent and independent variables
- independent variables do not need to be multivariate normal – although multivariate normality yields a more stable solution
- residuals do not need to be multivariate normally distributed
- homoscedasticity is not needed. Logistic regression does not need variances to be heteroscedastic for each level of the independent variables.
- Lastly, it can handle ordinal and nominal data as independent variables.  The independent variables do not need to be metric (interval or ratio scaled).
- Binary logistic regression requires the dependent variable to be binary and ordinal logistic regression requires the dependent variable to be ordinal.  

- the model should be fitted correctly.  Neither over fitting nor under fitting should occur.
- Fourthly, the error terms need to be independent.  Logistic regression requires each observation to be independent. 
- model should have little or no multicollinearity.
- logistic regression assumes linearity of independent variables and log odds
- it requires quite large sample sizes. 

DISTRIBUTION CHECKING
ORIGINAL VARIABLES
```{r}
#check the distribution of all original variables
par(mfrow = c(5,5), mar = c(2,3,1,1))
hist(rounds.nona$match, main = 'match')
hist(rounds.nona$wave_condition, main = 'wave_condition')
hist(rounds.nona$met_so_far, main = 'met_so_far')
hist(rounds.nona$int_corr, main = 'int_corr')
hist(rounds.nona$same_race, main = 'same_race')
hist(rounds.nona$same_country, main = 'same_country')
hist(rounds.nona$age_ratio, main = 'age_ratio')
hist(rounds.nona$met_before, main = 'met_before')
hist(rounds.nona$diff_pref_attractive, main = 'diff_pref_attr')
hist(rounds.nona$diff_pref_sincere, main = 'diff_pref_sinc')
hist(rounds.nona$diff_pref_intelligent, main = 'diff_pref_int')
hist(rounds.nona$diff_pref_fun, main = 'diff_pref_fun')
hist(rounds.nona$diff_pref_ambitious, main = 'diff_pref_amb')
hist(rounds.nona$diff_pref_sharedhobbies, main = 'diff_pref_shared')
hist(rounds.nona$rating_by_partner_attractive, main = 'rating_by_attr')
hist(rounds.nona$rating_by_partner_sincere, main = 'rating_by_sinc')
hist(rounds.nona$rating_by_partner_intelligent, main = 'rating_by_int')
hist(rounds.nona$rating_by_partner_fun, main = 'rating_by_fun')
hist(rounds.nona$rating_by_partner_ambitious, main = 'rating_by_amb')
hist(rounds.nona$rating_by_partner_sharedhobbies, main = 'rating_by_shared')
hist(rounds.nona$rated_partner_attractive, main = 'rated_attr')
hist(rounds.nona$rated_partner_sincere, main = 'rated_sinc')
hist(rounds.nona$rated_partner_intelligent, main = 'rated_fun')
hist(rounds.nona$rated_partner_fun, main = 'rated_int')
hist(rounds.nona$rated_partner_ambitious, main = 'rated_amb')
hist(rounds.nona$rated_partner_sharedhobbies, main = 'rated_shared')

```
```{r}
#check distribution for log and sqrt transformations
rounds.log <- rounds.nona
rounds.sqrt <- rounds.nona
names(rounds.log)
```

LOG TRANSFORMED
```{r}
#log transformation distributions
par(mfrow = c(5,5), mar = c(2,3,1,1))
rounds.log[,c(3,9:14)] <- log(rounds.log[,c(3,9:14)])
hist(rounds.log$match, main = 'match')
hist(rounds.log$wave_condition, main = 'wave_condition')
hist(rounds.log$met_so_far, main = 'met_so_far')
hist(rounds.log$int_corr, main = 'int_corr')
hist(rounds.log$same_race, main = 'same_race')
hist(rounds.log$same_country, main = 'same_country')
hist(rounds.log$age_ratio, main = 'age_ratio')
hist(rounds.log$met_before, main = 'met_before')
hist(rounds.log$diff_pref_attractive, main = 'diff_pref_attr')
hist(rounds.log$diff_pref_sincere, main = 'diff_pref_sinc')
hist(rounds.log$diff_pref_intelligent, main = 'diff_pref_int')
hist(rounds.log$diff_pref_fun, main = 'diff_pref_fun')
hist(rounds.log$diff_pref_ambitious, main = 'diff_pref_amb')
hist(rounds.log$diff_pref_sharedhobbies, main = 'diff_pref_shared')
hist(rounds.log$rating_by_partner_attractive, main = 'rating_by_attr')
hist(rounds.log$rating_by_partner_sincere, main = 'rating_by_sinc')
hist(rounds.log$rating_by_partner_intelligent, main = 'rating_by_int')
hist(rounds.log$rating_by_partner_fun, main = 'rating_by_fun')
hist(rounds.log$rating_by_partner_ambitious, main = 'rating_by_amb')
hist(rounds.log$rating_by_partner_sharedhobbies, main = 'rating_by_shared')
hist(rounds.log$rated_partner_attractive, main = 'rated_attr')
hist(rounds.log$rated_partner_sincere, main = 'rated_sinc')
hist(rounds.log$rated_partner_intelligent, main = 'rated_int')
hist(rounds.log$rated_partner_fun, main = 'rated_fun')
hist(rounds.log$rated_partner_ambitious, main = 'rated_amb')
hist(rounds.log$rated_partner_sharedhobbies, main = 'rated_shared')
```

SQRT TRANSFORMED
```{r}
#sqrt transformation distributions
par(mfrow = c(5,5), mar = c(2,3,1,1))
rounds.sqrt[,c(3,9:14)] <- sqrt(rounds.sqrt[,c(3,9:14)])
hist(rounds.sqrt$match, main = 'match')
hist(rounds.sqrt$wave_condition, main = 'wave_condition')
hist(rounds.sqrt$met_so_far, main = 'met_so_far')
hist(rounds.sqrt$int_corr, main = 'int_corr')
hist(rounds.sqrt$same_race, main = 'same_race')
hist(rounds.sqrt$same_country, main = 'same_country')
hist(rounds.sqrt$age_ratio, main = 'age_ratio')
hist(rounds.sqrt$met_before, main = 'met_before')
hist(rounds.sqrt$diff_pref_attractive, main = 'diff_pref_attr')
hist(rounds.sqrt$diff_pref_sincere, main = 'diff_pref_sinc')
hist(rounds.sqrt$diff_pref_intelligent, main = 'diff_pref_int')
hist(rounds.sqrt$diff_pref_fun, main = 'diff_pref_fun')
hist(rounds.sqrt$diff_pref_ambitious, main = 'diff_pref_amb')
hist(rounds.sqrt$diff_pref_sharedhobbies, main = 'diff_pref_shared')
hist(rounds.sqrt$rating_by_partner_attractive, main = 'rating_by_attr')
hist(rounds.sqrt$rating_by_partner_sincere, main = 'rating_by_sinc')
hist(rounds.sqrt$rating_by_partner_intelligent, main = 'rating_by_int')
hist(rounds.sqrt$rating_by_partner_fun, main = 'rating_by_fun')
hist(rounds.sqrt$rating_by_partner_ambitious, main = 'rating_by_amb')
hist(rounds.sqrt$rating_by_partner_sharedhobbies, main = 'rating_by_shared')
hist(rounds.sqrt$rated_partner_attractive, main = 'rated_attr')
hist(rounds.sqrt$rated_partner_sincere, main = 'rated_sinc')
hist(rounds.sqrt$rated_partner_intelligent, main = 'rated_int')
hist(rounds.sqrt$rated_partner_fun, main = 'rated_fun')
hist(rounds.sqrt$rated_partner_ambitious, main = 'rated_amb')
hist(rounds.sqrt$rated_partner_sharedhobbies, main = 'rated_shared')
```




```{r}
final <- rounds.sqrt
final$wave_condition <- as.numeric(as.character(final$wave_condition))
final$same_race <- as.numeric(as.character(final$same_race))
final$met_before <- as.numeric(as.character(final$met_before))
final$match <- as.factor(as.character(final$match))
str(final)
```
```{r}
summary(final)
```

```{r}
head(final)
```

```{r}
boxplot(final)
```

```{r}
indexes = sample(1:nrow(final), size=0.2*nrow(final))
train <- final[-indexes,]
test<- final[indexes,]
```

```{r}
# library(PerformanceAnalytics)
# chart.Correlation(rounds.nona, method = 'pearson', histogram = T, pch = 16)
```

```{r}
str(train)
```

```{r}
#we're picking sqrt transformation on some of the variables because they look better in terms of normal distribution
paste(names(train), collapse=' + ')
```

```{r}
library(MASS)
fit <- glm(match~., family = binomial(logit), data = train)
```

```{r}
summary(fit)
```

```{r}
#fit.step
library(ROCR)
fitpreds.orig <- predict(fit, test, type = 'response')
fitpred.orig <- prediction(fitpreds.orig, test$match)
fitperf.orig <- performance(fitpred.orig, "tpr","fpr")
plot(fitperf.orig, col = 'green', lwd =2, main = "ROC Curve for Logistic")
abline(a = 0, b = 1, lwd = 2, lty=2, col = 'gray')
auc.orig <- performance(fitpred.orig, measure = 'auc')
auc.orig <- auc.orig@y.values[[1]]

cat('AUC: ',auc.orig)

library(caret)

test$predorig <- ifelse(fitpreds.orig >0.5, 1,0)
confusionMatrix(test$predorig, test$match, positive = "1")

```

```{r}
fit.step <- step(fit)
```

```{r}
summary(fit.step)
```

```{r}
#removal of variables with high P-value
fit.step1 <- glm(formula = match ~ diff_pref_sharedhobbies + rating_by_partner_attractive + 
    rating_by_partner_fun + rating_by_partner_ambitious + rating_by_partner_sharedhobbies + 
    rated_partner_attractive + rated_partner_sincere + rated_partner_fun + 
    rated_partner_ambitious + rated_partner_sharedhobbies, family = binomial(logit), 
    data = train)
```

```{r}
summary(fit.step1)
```

```{r}
library(car)
vif(fit.step1)

#The variable inflation factor in the car package provides a useful means of checking multicollinearity. Multicollinearity is what happens when a given predictor in the model can be approximated by a linear combination of the other predictors in the model. This means that your inputs to the model are not independent of each other. This has the effect of increasing the variance of model coefficients. We want to decrease the variance to make our models more significant, more robust. That’s why it’s a good idea to omit variables from the model which exhibit a high degree of multicollinearity.

#
```

```{r}
durbinWatsonTest(fit.step1)
crPlots(fit.step)

#The first is the Durbin Watson test, which tests for correlated residuals (An assumption we make is for non-correllated residuals). We can also try the crPlots() function. It plots the residuals against the predictors, allowing us to see which categorical variables contributed the most to variance, or allowing us to spot possible patterns in the residuals on numerical variables.
```


With D-W statistic of 1.79273 and an associated p-value of 0, we fail to reject the null hypothesis that the errors are correlated. 


```{r}
#fit.step
library(ROCR)
fitpreds <- predict(fit.step1, test, type = 'response')
fitpred <- prediction(fitpreds, test$match)
fitperf <- performance(fitpred, "tpr","fpr")
plot(fitperf, col = 'green', lwd =2, main = "ROC Curve for Logistic")
abline(a = 0, b = 1, lwd = 2, lty=2, col = 'gray')
auc <- performance(fitpred, measure = 'auc')
auc <- auc@y.values[[1]]

cat('AUC: ',auc)
```

```{r}
library(caret)

test$pred <- ifelse(fitpreds >0.5, 1,0)
confusionMatrix(test$pred, test$match, positive = "1")

```


To evaluate the performance of a logistic regression model, we must consider few metrics. Irrespective of tool (SAS, R, Python) you would work on, always look for:

1. AIC (Akaike Information Criteria) – The analogous metric of adjusted R² in logistic regression is AIC. AIC is the measure of fit which penalizes model for the number of model coefficients. Therefore, we always prefer model with minimum AIC value.

2. Null Deviance and Residual Deviance – Null Deviance indicates the response predicted by a model with nothing but an intercept. Lower the value, better the model. Residual deviance indicates the response predicted by a model on adding independent variables. Lower the value, better the model.

3. Confusion Matrix: It is nothing but a tabular representation of Actual vs Predicted values. This helps us to find the accuracy of the model and avoid overfitting. This is how it looks like:


SOME DESCRIPTIVE CHARTS
```{r}
names(rounds)
names(participants)

descriptive <- merge(rounds, participants, by.x = 'iid_id', by.y = 'id', all.x = T)
```

```{r}
colnames(descriptive)[33:62] <- paste("iid",colnames(descriptive[,c(33:62)]), sep = "_")
names(descriptive)
```

```{r}
descriptive <- merge(descriptive, participants, by.x = "partner_id", by.y = "id", all.x = T)
names(descriptive)
```

```{r}
colnames(descriptive)[63:92] <- paste("partner",colnames(descriptive[,c(63:92)]), sep = "_")
names(descriptive)
```

```{r}
summary(descriptive)
```
```{r}
nomatch<- split(descriptive,descriptive$match)$'0'
yesmatch<- split(descriptive,descriptive$match)$'1'
```

```{r}
names(yesmatch)
```

```{r}
par(mfrow = c(1,3), mar = c(2.5,2,1,1))
boxplot(yesmatch[,c(34,64)], main = "Age", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(38,68)], main = "Romantic Goal", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(56,86)], main = "Expected Happiness", col = c('lightblue','orange'), names = c('Women','Men'))
```



```{r}
par(mfrow = c(3,5), mar = c(2.5,2,1,1))
boxplot(yesmatch[,c(41,71)], main = "Exercise", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(42,72)], main = "Dining", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(43,73)], main = "Museums", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(44,74)], main = "Art", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(45,75)], main = "Hiking", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(46,76)], main = "Gaming", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(47,77)], main = "Clubbing", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(48,78)], main = "Reading", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(49,79)], main = "TV", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(50,80)], main = "Theater", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(51,81)], main = "Movies", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(52,82)], main = "Concerts", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(53,83)], main = "Music", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(54,84)], main = "Shopping", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(55,85)], main = "Yoga", col = c('lightblue','orange'), names = c('Women','Men'))

#title("Comparison of Interests between Women and Men", outer=TRUE)
```

```{r}
par(mfrow = c(2,3), mar = c(2.5,2,1,1))
boxplot(yesmatch[,c(57,87)], main = "Attractiveness", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(58,88)], main = "Sincerity", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(59,89)], main = "Intelligence", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(60,90)], main = "Fun", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(61,91)], main = "Ambitiousness", col = c('lightblue','orange'), names = c('Women','Men'))
boxplot(yesmatch[,c(62,92)], main = "Shared Hobbies", col = c('lightblue','orange'), names = c('Women','Men'))
```

```{r}
library(fmsb)
library(tidyr)
summary(yesmatch[,c(41:55)])
statswoman <- as.data.frame(0.6264)
colnames(statswoman) <- 'exercise'
statswoman$dining <- mean(yesmatch[,42])
statswoman$museums <- mean(yesmatch[,43])
statswoman$art <- mean(yesmatch[,44])
statswoman$hiking <- mean(yesmatch[,45])
statswoman$gaming <- mean(yesmatch[,46])
statswoman$clubbing <- mean(yesmatch[,47])
statswoman$reading <- mean(yesmatch[,48])
statswoman$tv <- mean(yesmatch[,49])
statswoman$theater <- mean(yesmatch[,50])
statswoman$movies <- mean(yesmatch[,51])
statswoman$concerts <- mean(yesmatch[,52])
statswoman$music <- mean(yesmatch[,53])
statswoman$shopping <- mean(yesmatch[,54])
statswoman$yoga <- mean(yesmatch[,55])
statswoman

summary(yesmatch[,c(71:85)])
statsman <- as.data.frame(mean(yesmatch[,71]))
colnames(statsman) <- 'exercise'
statsman$dining <- mean(yesmatch[,72])
statsman$museums <- mean(yesmatch[,73])
statsman$art <- mean(yesmatch[,74])
statsman$hiking <- mean(yesmatch[,75])
statsman$gaming <- mean(yesmatch[,76])
statsman$clubbing <- mean(yesmatch[,77])
statsman$reading <- mean(yesmatch[,78])
statsman$tv <- mean(yesmatch[,79])
statsman$theater <- mean(yesmatch[,80])
statsman$movies <- mean(yesmatch[,81])
statsman$concerts <- mean(yesmatch[,82])
statsman$music <- mean(yesmatch[,83])
statsman$shopping <- mean(yesmatch[,84])
statsman$yoga <- mean(yesmatch[,85])
statsman
```

```{r}
statsman <- rbind(rep(1,15), rep(0,15), statsman)
statsman
statswoman <- rbind(rep(1,15), rep(0,15), statswoman)
statswoman
```

```{r}
women <- yesmatch[,c(41:55)]
men <- yesmatch[,c(71:85)]
colors_border=c( rgb(0.2,0.5,0.5,0.9), 
                 rgb(0.8,0.2,0.5,0.9) , 
                 rgb(0.7,0.5,0.1,0.9) )
colors_in=c( rgb(0.2,0.9,0.8,0.9), 
             rgb(0.8,0.2,0.5,0.4) , 
             rgb(0.7,0.5,0.1,0.4) )
colors_inw=c( rgb(0.9,0.5,0.5,0.4), 
             rgb(0.8,0.2,0.5,0.4) , 
             rgb(0.7,0.5,0.1,0.4) )

radarchart(statsman, axistype = 1,
    #custom polygon
    pcol=colors_border, 
    pfcol=colors_in,
    plwd = 4,
    plty = 1,
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=0.8,
    #custom labels
    vlcex=0.8)
radarchart(statswoman, axistype = 1,
    #custom polygon
    pcol=colors_border, 
    pfcol=colors_inw,
    plwd = 4,
    plty = 1,
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=0.8,
    #custom labels
    vlcex=0.8)
```

```{r}
prefwoman <- as.data.frame(mean(yesmatch[,57]))
colnames(prefwoman) <- 'Attractiveness'
prefwoman$Sincerity <- mean(yesmatch[,58])
prefwoman$Intelligence <- mean(yesmatch[,59])
prefwoman$Fun <- mean(yesmatch[,60])
prefwoman$Ambitious <- mean(yesmatch[,61])
prefwoman$SharedHobbies <- mean(yesmatch[,62])

prefwoman

prefman <- as.data.frame(mean(yesmatch[,87]))
colnames(prefman) <- 'Attractiveness'
prefman$Sincerity <- mean(yesmatch[,88])
prefman$Intelligence <- mean(yesmatch[,89])
prefman$Fun <- mean(yesmatch[,90])
prefman$Ambitious <- mean(yesmatch[,91])
prefman$SharedHobbies <- mean(yesmatch[,92])

prefman

prefman <- rbind(rep(1,15), rep(0,15), prefman)
prefman
prefwoman <- rbind(rep(1,15), rep(0,15), prefwoman)
prefwoman
```

```{r}
colors_border=c( rgb(0.2,0.5,0.5,0.9), 
                 rgb(0.8,0.2,0.5,0.9) , 
                 rgb(0.7,0.5,0.1,0.9) )
colors_in=c( rgb(0.2,0.9,0.8,0.9), 
             rgb(0.8,0.2,0.5,0.4) , 
             rgb(0.7,0.5,0.1,0.4) )
colors_inw=c( rgb(0.9,0.5,0.5,0.4), 
             rgb(0.8,0.2,0.5,0.4) , 
             rgb(0.7,0.5,0.1,0.4) )

radarchart(prefman, axistype = 1,
    #custom polygon
    pcol=colors_border, 
    pfcol=colors_in,
    plwd = 4,
    plty = 1,
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=0.8,
    #custom labels
    vlcex=0.8)
radarchart(prefwoman, axistype = 1,
    #custom polygon
    pcol=colors_border, 
    pfcol=colors_inw,
    plwd = 4,
    plty = 1,
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5), cglwd=0.8,
    #custom labels
    vlcex=0.8)
```

